\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-05 paper/draft.tex
Update text

@@

We have briefly introduced four motivating analyses for extracting information about an application's dependencies.
While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses systems as these

require highly specialized solutions often outside the core language,
do not leverage or offer semantic information at the level of module boundaries,
or lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
These applications clearly illustrate the need for a system 
To summarize, these applications would appear to be served well by a system that:
\begin{itemize}
  \item Operates at the level of modules, both semantics and performance-wise
  \item Does not require learning a new tool or language---on the contrary,
    developers
  \item can be bolt onto an existing runtime as a library, regardless of whether 
  \item supports programmable analyses
\end{itemize}

In the next section we describe the design \sys, a new dynamic analyses
framework that satisfies these goals

\section{Module-aware Dynamic Analysis}
\label{design}

\subsection{Overview}

FIXME: add user data
At a high level, module dialysis works at three stages:

@@

% \textbf{Core Language}
% a few is not the same as 
Transformations are used pervasively throughout \sys, and are abstracted via a few parametrizable templates.
Templates map different types of values (List.~\ref{core-tx}) to a generic handler for each type.
%given a value, a template will transform it using a handler matching its type
% Templates match, 
% \hl{match} between different \hl{value} % what are values
%    \emph{types} and define generic handlers for each type.
Transformations have these handlers parametrized to achieve concrete goals such as monitoring, serialization, and scale-out.
Simplified instances are described in the following two sections (\S\ref{profiling}--\ref{core}).

Transformations can be applied to any value in the language, such as an object returned from a module or an exception about to be sent across the network.
The general case of such a value is a directed acyclic graph (DAG).
The types of its vertices can be coarsely grouped into primitives, functions, and objects.
Objects map strings to other values, pointing to other vertices in the DAG.
% Listing~\ref{core-tx} presents a simplified core of the language.
Transformations start by walking the DAG from the root vertex and processing component values based on their types.
They do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.
They only partially explore the object graph, as they do not peak through function closure environments.
Fortunately, this aligns well with our goal of monitoring activity at module boundaries and ignoring module-internal activity.

As an example, consider transforming the \ttt{crypto} module~\sx{solution}.
\sys traverses the object returned by \ttt{crypto} and replaces functions such as \ttt{pbkdf2} with wrappers whose specifics depend on the intended goal:
  profiling wrappers call the original function in between statistics collection, and RPC wrappers forward the call to a remote replica.

@@

\heading{Dynamic Analysis Systems}
There are several dynamic analysis frameworks for JavaScript~\cite{javascript1, javascript2, javascript3, mugshot, jalangi}.
The two most popular, Jalangi~\cite{jalangi} and Mugshot~\cite{mugshot}, are fine-grained code-level instrumentation tools.
On top of analysis, their heavy instrumentation is powerful enough to record and replay entire program executions.
This power comes at a significant performance cost---typically 2--3 order-of-magnitude slowdown---as they need to virtualize the entire execution environment:
  source-code-level rewriting every expression corresponding to a profiling event in the original program needs is resolves to a profiling function call.
They are also not embeddable in existing applications in a runtime-agnostic manner.
These features are contrary to \sys, which leverages fairly basic programming-language techniques such as variable shadowing and context transformation during library loading to insert analysis hooks completely transparently to the runtime environment.

NodeProf~\cite{javascript3} is a fine-grained dynamic analysis implemented using Truffle~\cite{} and running on top of Graal.js [28], a Node.js-compatible runtime.
NodeProf takes a different approach than code-level instrumentation, statically instrumenting the AST, which makes it easier to maintain compared to source changes.
Similar to \sys, NodeProf 
is not tied to the source code, has significantly lower overheads, and can be toggled on/off during program execution.
Requires AST extraction and manipulation to build, which is not available in many languages % it is an additional requirement
and is in conflict with many dynamic features. 
It stands at a different point in the design space---more powerful analysis, but with significantly more effort:
  assumes knowledge of the internal Graal and Truffle APIs and requires recompilation of the Java hooks.

Similar to NodeProf, \sys

Aran~\cite{javascript1} is presented in a poster to

JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework, similar to \sys's analysis \fixme{A2}, build around proxies.
It allows users to write 
It illustrates the need for a general-purpose framework such as \sys, as many of JSConTest2's access permission contracts are 
Our evaluation shows that this analysis (and others) can be implemented on top of \sys with significantly less effort.

>>>>

\newcommand{\goal}[1]{(\textbf{G#1})\xspace}

@@

We have briefly introduced four motivating analyses for extracting information about an application's dependencies.
While the challenges behind these analyses share several characteristics, today they remain largely unaddressed by dynamic analyses frameworks due to a combination of factors:
  these frameworks either require highly specialized solutions often outside the core language,
  do not leverage or offer semantic information at the level of module boundaries, or
  lead to a high (often impractical) performance overheads due to the high granularity of their analyses.
To summarize, these applications would appear to be served well by a system that:
\begin{itemize}
  \item \textbf{(G1)} Operates at the level of modules, leveraging both the semantics and performance potential that this level of granularity potentially offers.
  \item \textbf{(G2)} Does not require learning a new tool or language, but rather allows developers to express their analyses on the same language as the program.
  \item \textbf{(G3)} Can be implemented as a library that bolts onto an existing language runtime environment.
\end{itemize}

The next section describes program dialysis, a new program analysis technique that satisfies these goals, in a language-agnostic manner~\sx{design};
  the section following that describes a concrete implementation for the server-side JavaScript ecosystem~\sx{impl}.

\section{The Design of Program Dialysis}
\label{design}

Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
  instead of simply locating a library in the filesystem and loading it, it yields control to \sys which applies a series of transformation steps to libraries, with the goal of interposing at their boundaries.
We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
We next describe each one of these steps in more detail~(\S\ref{one}--\ref{three}).

\subsection{Overview}
\label{overview}

% FIXME: add user data
At a high level, the goal of program dialysis is to \fra the program at the boundaries of third-party modules, apply transformations that insert analysis-specific machinery, and then carefully \ass individual components to maintain the original semantics.
 In more detail, these three phases are as follows:

@@

Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.

% , such as an object returned from a module or an exception about to be sent across the network.
Transformations can be applied to any value in the language. 
The most general value is an object, a bag of records holding key-value fields;
  other value types include primitives, functions, and booleans.
% Listing~\ref{core-tx} presents a simplified core of the language.
Transformations walk objects from their root, processing component values based on their types (Fig.~\ref{fig:txfm}).
More specifically,
  (i) \emph{function} values are wrapped by closures specific to the goal of the transformation; % on the function's arguments and return values;
  (ii) \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.

The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
These skeletons provide hooks for end-developers writing analyses.
Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
These hooks are then extended or rewritten by developers to

For example, consider transforming a \ttt{Math} object with the goal of profiling its interfaces or generating a remote interface (Fig.~\ref{fig:lib}\emph{a,b}).
\sys traverses the object returned by \ttt{Math} and replaces functions such as \ttt{div} with wrappers.
The wrappers depend on the intended goal:
  profiling wrappers would record invocation statistics, and RPC wrappers would forward calls to a remote replica.

\subsection{Disassembly}
\label{one}

\subsection{Transformation}
\label{two}

\subsection{Reassembly}
\label{three}

@@

% \heading{Dynamic Analysis Systems}
There are several dynamic analysis frameworks for JavaScript~\cite{javascript1, javascript2, javascript3, mugshot, jalangi}.
The two most popular, Jalangi~\cite{jalangi} and Mugshot~\cite{mugshot}, are fine-grained code-level instrumentation tools.
On top of analysis, their heavy instrumentation is powerful enough to record and replay entire program executions.
This power comes at a significant performance cost---typically 2--3 order-of-magnitude slowdown---as they need to virtualize the entire execution environment:
  source-code-level rewriting every expression corresponding to a profiling event in the original program needs is resolves to a profiling function call.
They are also not embeddable in existing applications in a runtime-agnostic manner.
These features are contrary to \sys, which leverages fairly basic programming-language techniques such as variable shadowing and context transformation during library loading to insert analysis hooks completely transparently to the runtime environment.

NodeProf~\cite{javascript3} is a fine-grained dynamic analysis implemented using Truffle~\cite{} and running on top of Graal.js [28], a Node.js-compatible runtime.
NodeProf stands at a different point in the analysis design space---more powerful than \sys, but with significantly more effort.
It statically instruments the program's AST (rather than the code), making it easier to maintain compared to source changes but assuming some knowledge of the Graal and Truffle APIs and requiring recompilation of the Java hooks.
Different from \sys, it leverages AST extraction and manipulation to build, which is not available in many languages and may be limit by dynamic features such as reflection and JITing.
Nevertheless, NodeProf's approach shares similarities with \sys, including decoupling from the source code, overheads lower than code instrumentation, and can on/off toggling during execution.
%FIXME: Lya is also limited (i) by dynamic features such as reflection, because they're gonna hit the wrapper and (ii) the equality and other primitive operators

Aran~\cite{javascript1}, an implementation sketch of proxy-based analysis, leverages JavaScript's \ttt{with} primitive to wrap custom contexts.
\sys works at the module boundaries (at a potentially coarser granularity) without any special language constructs.

JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework, similar to \sys's analysis \fixme{A2}, build around proxies.
It allows users to write access control contracts, policies that execute at runtime.
It illustrates the need for a general-purpose framework such as \sys, as many of JSConTest2's access permission contracts are 
Our evaluation shows that this analysis (and others) can be implemented on top of \sys with significantly less effort.
